### 2023-03-23 Documentation/WT group/NHL/Introduction/Introduction.tex
documentation

@@

\begin{figure}[H]
    \centering
    \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
    \caption{EHDA automation system setup}
    \label{fig:microdripping_current_pic}
  \end{figure}

>>>>

\section{Droplet Formation}
\label{sec:drop_formation}

In the Aerosol reasearch community there is a branch of studies about droplets formation. In the droplet field a very functional for applications is the atomization, which refers to breaking the liquid in small droplets.
There is many ways of atomizing a liquid. Some using mechanical energy such as ultrassound, rotating disk\cite{Disk_atomization}, pressure or blowing air on the meniscus. But also, some of them using electric forces such as electrospray atomization.

For

@@

Since the beginning of EHDA until today the researchs are being conducted manually with visual classification of the spraying mode using a camera or even by naked eyes.
It is recommended to use a high speed (HS) camera because some dripping or intermittent states can be in a high frequency and be wrongly noticed as a stable condition.
The setup in \ref{fig:ehda_setup} shows the most common setup used for EHDA researchers.

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/system_setup.png}}
  \caption{EHDA experiment setup \cite{Luewton}}
  \label{fig:ehda_setup}
\end{figure}

Therefore some researchs were made about the classification of the spraying mode measuring the current flowing through the nozzle to plate\cite{Sjaaks}\cite{Chen_Pui}. That current signal holds a lot o information 
about the dynamics that is happening with the liquid. In \ref{fig:microdripping_current_pic} we can see an example of that. It's clear the two droplets generated in this time frame.

\begin{figure}[H]
    \centering
    \resizebox{150mm}{!}{\includegraphics{Figuras/report2/img2.png}}
    \caption{Current measurement sample of a micro-dripping spraying mode. This graph represents 0.5s sample. The sampling frequency is 100kHz. Hence we have 50000 current values.}
    \label{fig:microdripping_current_pic}
  \end{figure}

### 2023-03-23 Documentation/WT group/NHL/Metodology/Metodology.tex
documentation

@@

\begin{figure}[thpb]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
  \caption{EHDA automation system setup}
  \label{fig:control_model_fig}
\end{figure}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=5cm]{Figuras/report4/json_structure.png}
            \caption{Output data json structure}
        \end{figure}

@@

 According to \cite{Sjaaks} evaluating the current data flowing through the nozzle to the plate we can analyze the signa that represents the spraying dynamics.
 through statistical analysis in this signal such as mean value and standart deviation we can analyze if the signal is stable or not.

 Our classification by statistical analysis was implemented in the automation library made by the previous student \cite{Monica}.

>>>>

\begin{figure}[H]
    \centering
    \resizebox{150mm}{!}{\includegraphics{Figuras/report4/experiment_print1.png}}
    \caption{EHDA automation system setup}
    \label{fig:metodology_example1}
\end{figure}

%   \begin{figure}[H]
%     \centering
%     \resizebox{150mm}{!}{\includegraphics{Figuras/report4/multi_jet_print.png}}
%     \caption{EHDA automation system setup}
%     \label{fig:metodology_example2}
% \end{figure}

@@

\begin{figure}[H]
  \centering
  \resizebox{150mm}{!}{\includegraphics{Figuras/control_loop.png}}
  \caption{EHDA automation system setup}
  \label{fig:control_model_fig}
\end{figure}

@@

        \begin{figure}[H]
            \center
            \includegraphics[width=10cm]{Figuras/19:03/new_sample.png}
            \caption{Output data json structure}
        \end{figure}

@@

 According to Sjaaks\cite{Sjaaks}, evaluating the current data flowing through the nozzle to the plate can give us valuable information about the spraying behaviour.
 Together with the current characteristics, visual observations and results from literature it was investigated whether generic trends are present that can be related to the actual spraying modes.
 It was concluded that factors like geometry, polarity, material properties and occurring discharges are reflected in the system current.
In this work, the author also exposed some signal characteristics that can be used to classify the actual spraying mode with a sample of measured current using both time domain and frequency domain analysis.

From those analysis we are appliying in our automatic classification system the relative standard deviation. Which is refered as the sample standart deviation divided by the sample mean values.

 through statistical analysis in the signal such as mean value and standart deviation.
 Our classification by statistical analysis was implemented in the automation library made by the previous student \cite{Monica}.
